Near Optimal Behavior with Approximate State Abstraction

### 2016-02-04 paper/abstract.tex
Beep boop new intro and abstract

The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction. Prohibitively difficult task representations can be condensed such that essential information is preserved, and consequently, solutions are tractably computable. However, perfect abstractions are often computationally intractable and ineffective in environments where no two situations are exactly alike. For these reasons, we investigate approximate abstractions, which treat nearly-identical situations as equivalent. In this work, we characterize sufficient conditions for approximate abstractions that preserve near optimal behavior while reducing the complexity of the original task representation. We present theoretical guarantees of the quality of behaviors derived from four classes of approximate abstractions. Additionally, we empirically demonstrate that approximate abstractions lead to reduction in task complexity and bounded loss of optimality of behavior in a variety of environments. % Environments could also be tasks/problems/etc

>>>>

The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction. Prohibitively difficult task representations can be condensed such that essential information is preserved, and consequently, solutions are tractably computable. However, perfect abstractions, which treat fully-identical situations as equivalent, are often computationally intractable and ineffective in environments where no two situations are exactly alike. For these reasons, we investigate approximate abstractions, which treat nearly-identical situations as equivalent. In this work, we characterize sufficient conditions for approximate abstractions that preserve near optimal behavior while reducing the complexity of the original task representation. We present theoretical guarantees of the quality of behaviors derived from four classes of approximate abstractions. Additionally, we empirically demonstrate that approximate abstractions lead to reduction in task complexity and bounded loss of optimality of behavior in a variety of environments. % Environments could also be tasks/problems/etc

### 2016-02-04 paper/introduction.tex
Beep boop new intro and abstract

\section{Introduction}
Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant. Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction. However, perfect abstractions, which treat fully identical situations alike, require complete knowledge that is often computationally intractable. Furthermore, in natural environments, no two states are identical, so perfect abstraction is ineffective. To overcome these issues we investigate approximate abstractions that enable agents to treat sufficiently similar states as identical. This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.

We now ground all this stuff in MDPs and stuff.

@@

% Thesis: Approximate abstraction for three reasons.
The thesis of this work is that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy. Relaxing the aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits. First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}.

Second, because of their relaxed criteria of equality, approximate abstractions can achieve greater degrees of compression than perfect abstractions. This is particularly important in natural environments where no two states are identical.

Third, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation by adjusting what they consider sufficiently similar states.

>>>>

\section{Introduction}
Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant. Consequently, agents are able to solve considerably more complex problems than they would be able to without the use of abstraction. However, perfect abstractions, which treat fully-identical situations alike, require complete knowledge that is often computationally intractable. Furthermore, in natural environments, no two states are identical, so perfect abstraction is ineffective. To overcome these issues we investigate approximate abstractions that enable agents to treat sufficiently similar states as identical. This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.

\dnote{Want a clause, sentence, prhase, paragraph, that transitions us from the super high level biz in the first paragraph to the second paragraph}
Abstraction in the context of planning and \ac{RL} in an \ac{MDP} takes the form of state aggregation. \dnote{rephrase and add a sentence or two that gets us to paragraph two}

@@

% Thesis: Approximate abstraction for three reasons.
The thesis of this work is that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy. Relaxing the aggregation criteria from equality of quantities to $\epsilon$-closeness offers three benefits. First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}. Second, because of their relaxed criteria, approximate abstractions can achieve greater degrees of compression than perfect abstractions. This is particularly important in natural environments where no two states are identical. \dnote{note this in empirical results discussion, that random is sort of like a natural environment and when eps is 0, no compression} Third, because the state aggregation criteria are relaxed to approximate equality, they are able to tune the aggressiveness of abstraction by adjusting what they consider sufficiently similar states.
